---
title: "combined"
author: |
  | Chai Kau Yu, Davion (S2019226)
  | William Heng Chun Meng (S2005592)
  | Lim Mei Cee (17162537)
  | Kamal Suria Asri Raja (S2110703)
  | Hong Zi Shen (S2114600)
date: "`r format(Sys.time(), '%d/%m/%y')`"
output:
    prettydoc::html_pretty:
    theme: HPSTR
    highlight: github
    math: katex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

# Introduction+Clean/Preprocessing (Mei Cee)

```{r mei_cee, echo=TRUE, results='markup'}
df_country <- read.csv("models/cases_malaysia.csv", header=TRUE)
df_state <- read.csv("models/cases_state.csv", header=TRUE)
```

# Map (Zi Shen)

```{r import_libraries, message=FALSE, warning=FALSE}
if (!require("dplyr")) {
  install.packages("dplyr", repos = "https://cran.asia/")
}
if (!require("kableExtra")) {
  install.packages("kableExtra", repos = "https://cran.asia/")
}
# if (!require("lubridate"))
#   install.packages("lubridate", repos="https://cran.asia/");
if (!require("plotly")) {
  install.packages("plotly", repos = "https://cran.asia/")
}
if (!require("plyr")) {
  install.packages("plyr", repos = "https://cran.asia/")
}
if (!require("raster")) {
  install.packages("raster", repos = "https://cran.asia/")
}
if (!require("scales")) {
  install.packages("scales", repos = "https://cran.asia/")
}
if (!require("thematic")) {
  install.packages("thematic", repos = "https://cran.asia/")
}

library(dplyr)
library(kableExtra)
library(plotly)
library(plyr)
library(raster)
library(scales)
```

#### Data Ingestion

```{r data_ingestion, echo=TRUE, results='markup', result='asis'}
# covid_malaysia_endpoint <- "https://raw.githubusercontent.com/MoH-Malaysia/covid19-public/main/epidemic/cases_malasia.csv"
# covid_state_endpoint <- "https://raw.githubusercontent.com/MoH-Malaysia/covid19-public/main/epidemic/cases_state.csv"
covid_malaysia_endpoint <- "models/cases_malaysia.csv"
covid_state_endpoint <- "models/cases_state.csv"

df <- read.csv(covid_malaysia_endpoint, header = TRUE)
df_state <- read.csv(covid_state_endpoint, header = TRUE)
```

#### Data Initialization

```{r data_initialization, echo=TRUE, results='markup', result='asis'}
df_population <- data.frame(
  c("Selangor", "Sabah", "Johor", "Sarawak", "Perak", "Kedah", "Kelantan", "Pulau Pinang", "W.P. Kuala Lumpur", "Pahang", "Terengganu", "Negeri Sembilan", "Melaka", "Perlis", "W.P. Putrajaya", "W.P. Labuan"),
  c(6555400, 3833000, 3794000, 2822200, 2508900, 2194100, 1928800, 1774400, 1746600, 1684600, 1275100, 1129100, 937500, 255400, 116100, 100100)
)
colnames(df_population) <- c("NAME_1", "pop")

theme_opts <- list(theme(
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  plot.background = element_blank(),
  axis.line = element_blank(),
  axis.text.x = element_blank(),
  axis.text.y = element_blank(),
  axis.ticks = element_blank(),
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  plot.title = element_blank()
))

malaysia <- getData("GADM", country = "MYS", level = 1)
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Trengganu", "Terengganu"))
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Kuala Lumpur", "W.P. Kuala Lumpur"))
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Labuan", "W.P. Labuan"))
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Putrajaya", "W.P. Putrajaya"))
malaysia@data$id <- rownames(malaysia@data)
```

#### Data Inspection

```{r data_inspection, echo=TRUE, results='markup', result='asis'}
# Check the structure of the dataframe
str(df)
str(df_state)

# Check the dimension of the dataframe
dim(df)
dim(df_state)

# Check the first 6 rows
head(df) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
head(df_state) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)

# Examine the statistics data
summary(df) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
summary(df_state) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
```

#### Handle missing/duplicate values

```{r handle_missing, echo=TRUE, results='markup', result='asis'}
# Check for the columns with missing values
colSums(is.na(df)) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
colSums(is.na(df_state)) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)

# Show first few rows of the missing values
head(df[rowSums(is.na(df)) > 0, ]) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
head(df[rowSums(is.na(df_state)) > 0, ]) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)

# The missing rows for df can be ignored as there are 2020 data. 2021 data contains more columns.
# There is no missing rows for df_state.

# Check for duplicate values
df[duplicated(df)]
df[duplicated(df_state)]

# There are no duplicated rows
```

#### Preprocessing

```{r preprocessing, echo=TRUE, results='markup', result='asis'}
# Change date type from String to Date
df$date <- as.Date(df$date, format = "%Y-%m-%d")
df_state$date <- as.Date(df_state$date, format = "%Y-%m-%d")
```

#### Total Cases

```{r total_cases, echo=TRUE, results='markup', class.source = 'fold-hide'}
  df_total_cases <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    mutate(cases_total = cases_total / 1000) %>%
    arrange(state) %>%
    dplyr::rename(NAME_1 = state)

  malaysia_map <- data.table::copy(malaysia)
  malaysia_map@data <- join(malaysia_map@data, df_total_cases, by = "NAME_1")
  malaysia_df <- fortify(malaysia_map)
  malaysia_df <- join(malaysia_df, malaysia_map@data, by = "id")

  # https://garthtarr.github.io/meatR/ggplot_extensions.html
  # https://rstudio-pubs-static.s3.amazonaws.com/160207_ebe47475bb7744429b9bd4c908e2dc45.html
  ggplot() +
    geom_polygon(data = malaysia_df, aes(x = long, y = lat, group = group, fill = cases_total), color = "white", size = 0.25) +
    theme(aspect.ratio = 2 / 5) +
    scale_fill_distiller(name = "No. of Total Cases (in '000)", palette = "YlOrRd", direction = 1, breaks = pretty_breaks(n = 5)) +
    labs(title = "Total Cases Since Day 1") +
    theme_opts


  df_total_cases <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    arrange(desc(cases_total))
```

#### Infection Rate

```{r infection_rate, echo=TRUE, results='markup', class.source = 'fold-hide'}
  df_infection_rate <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    dplyr::rename(NAME_1 = state) %>%
    join(df_population, by = "NAME_1") %>%
    mutate(rate = cases_total / pop) %>%
    arrange(NAME_1)

  malaysia_map <- data.table::copy(malaysia)
  malaysia_map@data <- join(malaysia_map@data, df_infection_rate, by = "NAME_1")
  malaysia_df <- fortify(malaysia_map)
  malaysia_df <- join(malaysia_df, malaysia_map@data, by = "id")

  # https://garthtarr.github.io/meatR/ggplot_extensions.html
  # https://rstudio-pubs-static.s3.amazonaws.com/160207_ebe47475bb7744429b9bd4c908e2dc45.html
  ggplot() +
    geom_polygon(data = malaysia_df, aes(x = long, y = lat, group = group, fill = rate), color = "white", size = 0.25) +
    theme(aspect.ratio = 2 / 5) +
    scale_fill_distiller(name = "No. of Total Cases (%)", palette = "YlOrRd", direction = 1, breaks = pretty_breaks(n = 5), labels = percent) +
    labs(title = "Infection Rate based on Total Population") +
    theme_opts

  df_infection_rate <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    dplyr::rename(NAME_1 = state) %>%
    join(df_population, by = "NAME_1") %>%
    dplyr::rename(state = NAME_1) %>%    
    mutate(rate = cases_total / pop) %>%
    arrange(desc(rate)) %>%
    mutate(rate = paste0(round(cases_total / pop * 100, 2), "%"))
```
# ARIMA (Kamal)

```{r kamal, echo=TRUE, results='markup'}

# Performing ARIMA on the number of COVID cases in Malaysia
# Aim to predict the next 60 days of new cases based on historical data

# import libraries

library(readxl)
library(dplyr)
library(ggplot2)
library(lubridate)
library(forecast)
library(fpp)
library(tseries)


# Import dataset

df_country <- read.csv("models/cases_malaysia.csv", header=TRUE)
df_state <- read.csv("models/cases_state.csv", header=TRUE)
```

```{r data_cleaning}
# A bit of cleaning
mycovidnewcases = df_country[,c(1:2)]
colnames(mycovidnewcases)
str(mycovidnewcases)
head(mycovidnewcases)

mycovidnewcases$date = as.Date(mycovidnewcases$date, format = "%d/%m/%Y")

covidplot = ggplot(mycovidnewcases, aes(date, cases_new)) +
  geom_line()
covidplot
```

# Plot ACF and PACF to understand the correlation in a time series data.
# Autocorrelation is the correlation between a time series and a delayed version of itself (lag).
# Autocorrelation Function (ACF) plots the correlation coefficient against the lag.
# The Partial Autocorrelation captures a 'direct' correlation between time series and a lagged version of itself

```{r check_seasonal_and_differencing}
# Perform ADF and KPSS test to check stationarity
# Null hypothesis is that the series is not stationary.

adf = adf.test(mycovidnewcases[,2])
adf
kpss = kpss.test(mycovidnewcases[,2])
kpss
```

# the ADF and KPSS test suggests that the data is non-stationary and differencing is required.
# Split data into train and test set. 

```{r split_train_test}
training = mycovidnewcases[1:500,]
test = mycovidnewcases[501:709,]
```

# Check how many differencing is needed

```{r check_differencing}

ndiffs(training[,2])  # Differencing of one is required but ARIMA model will do this for us as long as we input correct order (value of d)

```

# Use auto.arima to find out best model

```{r auto_arima}
summary(auto.arima(training[,2], trace = TRUE, ic = 'aicc', approximation = FALSE, stepwise = FALSE)) # Best model and order: ARIMA (3,1,2)
```

# Train the model with selected ARIMA model

```{r train_model}
trainingmodel = Arima(training[,2], order = c(3,1,2))
summary(trainingmodel)
coeftest(trainingmodel)
acf(trainingmodel$residuals)
```

# Make prediction using test set with the training model

```{r prediction}
testpred = forecast(test[,2], model = trainingmodel, h = 60, levels = c(95))
summary(testpred)
plot(testpred)
grid(nx = NULL, ny = NULL,
     lty = 2,
     col = 'gray',
     lwd = 2)
accuracy(testpred)
```

# END ---


# With rolling average,

```{r import}
library(zoo)
```

# Rolling average of 7

```{r rolling_7}
mycovidroll7 = mycovidnewcases %>%
  mutate(seven_avg = rollmean(mycovidnewcases[,2], 7, align = 'left', fill = 0)) %>%
  relocate(seven_avg)

head(mycovidroll7)

ggplot(mycovidroll7, aes(date, mycovidnewcases[,2])) + 
  geom_col(fill = 'pink') + 
  geom_line(aes(y = seven_avg), color = 'red', size = 0.75) +
  geom_line(aes(y = mycovidnewcases[,2]), color = 'blue', size = 1) + 
  labs(title = 'MY COVID data', y = 'covid cases')
```

# Rolling average of 21 

```{r rolling_21}
mycovidroll21 = mycovidnewcases %>%
  mutate(twoone_avg = rollmean(mycovidnewcases[,2], 21, align = 'left', fill = 0)) %>%
  relocate(twoone_avg)

ggplot(mycovidroll21, aes(date, mycovidnewcases[,2])) + 
  geom_col(fill = 'pink') + 
  geom_line(aes(y = mycovidroll7$seven_avg), color = 'red', size = 0.75) +
  geom_line(aes(y = mycovidnewcases[,2]), color = 'blue', size = 1) + 
  geom_line(aes(y = twoone_avg), color = 'green', size = 0.9) +
  labs(title = 'MY COVID data', y = 'covid cases')

tail(mycovidroll21, 30)
```

# ADF and KPSS test

```{r adfkpss}
adf21 = adf.test(mycovidroll21[,3])
adf21
kpss21 = kpss.test(mycovidroll21[,3])
kpss21

training21 = mycovidroll21[1:480,]
test21 = mycovidroll21[481:688,]
```

# Check differencing

```{r differencing}
ndiffs(training21[,3]) # one differencing
```

# Find best ARIMA model

```{r autoarima}
summary(auto.arima(training21[,3], trace = TRUE, ic = 'aicc', approximation = FALSE, stepwise = FALSE)) # Best model and order: ARIMA (2,1,2)
```

# Train model

```{r train}
trainingmodel21 = Arima(training21[,3], order = c(2,1,2))
summary(trainingmodel)
coeftest(trainingmodel)
acf(trainingmodel$residuals)
```

# Make prediction

```{r prediction_rolling21}
testpred21 = forecast(test21[,3], model = trainingmodel21, h = 30, levels = c(95))
summary(testpred21)
plot(testpred21)
grid(nx = NULL, ny = NULL,
     lty = 2,
     col = 'gray',
     lwd = 2)
accuracy(testpred21)
```

# Mixed Model (Davion)

```{r davion, echo=TRUE, results='markup'}
df_country <- read.csv("models/cases_malaysia.csv", header=TRUE)
df_state <- read.csv("models/cases_state.csv", header=TRUE)
```

# Closing (William)

```{r william, echo=TRUE, results='markup'}
df_country <- read.csv("models/cases_malaysia.csv", header=TRUE)
df_state <- read.csv("models/cases_state.csv", header=TRUE)
```


