---
title: "A Deep Analysis of Malaysian Covid-19 Cases in 2021"
author: |
  | Chai Kau Yu, Davion (S2019226)
  | William Heng Chun Meng (S2005592)
  | Lim Mei Cee (17162537)
  | Kamal Suria Asri Raja (S2110703)
  | Hong Zi Shen (S2114600)
date: "`r format(Sys.time(), '%d/%m/%y')`"
output:
    prettydoc::html_pretty:
    theme: HPSTR
    highlight: github
    math: katex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

### A series of R packages and libraries are installed beforehand. 

```{r import_libraries, message=FALSE, warning=FALSE}
if (!require("caret")) {
  install.packages("caret", repos = "https://cran.asia/")
}
if (!require("dplyr")) {
  install.packages("dplyr", repos = "https://cran.asia/")
}
if (!require("forecast")) {
  install.packages("forecast", repos = "https://cran.asia/")
}
if (!require("fpp")) {
  install.packages("fpp", repos = "https://cran.asia/")
}
if (!require("ggplot2")) {
  install.packages("ggplot2", repos = "https://cran.asia/")
}
if (!require("gridExtra")) {
  install.packages("gridExtra", repos = "https://cran.asia/")
}
if (!require("kableExtra")) {
  install.packages("kableExtra", repos = "https://cran.asia/")
}
if (!require("lubridate")) {
  install.packages("lubridate", repos="https://cran.asia/")
}
if (!require("plotly")) {
  install.packages("plotly", repos = "https://cran.asia/")
}
if (!require("plyr")) {
  install.packages("plyr", repos = "https://cran.asia/")
}
if (!require("raster")) {
  install.packages("raster", repos = "https://cran.asia/")
}
if (!require("readxl")) {
  install.packages("readxl", repos = "https://cran.asia/")
}
if (!require("scales")) {
  install.packages("scales", repos = "https://cran.asia/")
}
if (!require("tidyquant")) {
  install.packages("tidyquant", repos = "https://cran.asia/")
}
if (!require('tidyr')) {
  install.packages('tidyr', repos = "https://cran.asia/")
}
if (!require("thematic")) {
  install.packages("thematic", repos = "https://cran.asia/")
}
if (!require("tseries")) {
  install.packages("tseries", repos = "https://cran.asia/")
}
if (!require("zoo")) {
  install.packages("zoo", repos = "https://cran.asia/")
}


library(caret)
library(dplyr)
library(forecast)
library(fpp)
library(ggplot2)
library(gridExtra)
library(kableExtra)
library(lubridate)
library(plotly)
library(plyr)
library(raster)
library(readxl)
library(scales)
library(tidyquant)
library(tidyr)
library(tseries)
library(zoo)
```

# Introduction

### Coronavirus disease (COVID-19) is an infectious disease caused by the SARS-CoV-2 virus. WHO first learned of this new virus on 31 December 2019, following a report of a cluster of cases of ‘viral pneumonia’ in Wuhan, People’s Republic of China. The virus has been mutated over time resulting in second wave, thrid wave and beyond. This has also lead to "vaccine breakthrough infection" which occurs after a person has been fully vaccinated. That being said, this pandemic is still worrying people globally, so does the number of daily active cases.

# Objectives

### In this project, there are two objectives to be achieved: 
* To predict the number of daily active cases
* To compare the performance of ARIMA model, Linear Regression and Poisson Distribution

# Data Cleaning and Processing

### Based on the aforementioned objectives, two datasets "cases_malaysia.csv" and "cases_state.csv" were obtained from  https://github.com/MoH-Malaysia/covid19-public and imported to RStudio for further processing to carry out Exploraroty Data Analysis (EDA).

#### Data Ingestion

```{r data_ingestion, echo=TRUE, results='markup', result='asis'}
# covid_malaysia_endpoint <- "https://raw.githubusercontent.com/MoH-Malaysia/covid19-public/main/epidemic/cases_malasia.csv"
# covid_state_endpoint <- "https://raw.githubusercontent.com/MoH-Malaysia/covid19-public/main/epidemic/cases_state.csv"
covid_malaysia_endpoint <- "models/cases_malaysia.csv"
covid_state_endpoint <- "models/cases_state.csv"

df <- read.csv(covid_malaysia_endpoint, header = TRUE)
df_state <- read.csv(covid_state_endpoint, header = TRUE)
```

```{r data_ingestion_davion, echo=TRUE, results='markup'}
df_country <- read.csv("models/cases_malaysia.csv", header=TRUE)
# Convert date column & sort
df_country$date <- as.Date(df_country$date, format="%Y-%m-%d")
df_country <- df_country[order(df_country$date),]
# Filter data
df_data <- df_country[,c("date", "cases_new", "cases_active")]
```

#### Data Initialization

```{r data_initialization, echo=TRUE, results='markup', result='asis'}
df_population <- data.frame(
  c("Selangor", "Sabah", "Johor", "Sarawak", "Perak", "Kedah", "Kelantan", "Pulau Pinang", "W.P. Kuala Lumpur", "Pahang", "Terengganu", "Negeri Sembilan", "Melaka", "Perlis", "W.P. Putrajaya", "W.P. Labuan"),
  c(6555400, 3833000, 3794000, 2822200, 2508900, 2194100, 1928800, 1774400, 1746600, 1684600, 1275100, 1129100, 937500, 255400, 116100, 100100)
)
colnames(df_population) <- c("NAME_1", "pop")

theme_opts <- list(theme(
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  plot.background = element_blank(),
  axis.line = element_blank(),
  axis.text.x = element_blank(),
  axis.text.y = element_blank(),
  axis.ticks = element_blank(),
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  plot.title = element_blank()
))

malaysia <- getData("GADM", country = "MYS", level = 1)
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Trengganu", "Terengganu"))
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Kuala Lumpur", "W.P. Kuala Lumpur"))
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Labuan", "W.P. Labuan"))
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Putrajaya", "W.P. Putrajaya"))
malaysia@data$id <- rownames(malaysia@data)
```

#### Data Inspection
#### This is to obtain an overall understanding on the selected datasets of its strucutre and data context such as data types as well as to have a glance of minimum value, maximum value, median and mean of each of the columns.

```{r data_inspection, echo=TRUE, results='markup', result='asis'}
# Check the structure of the dataframe
str(df)
str(df_state)

# Check the dimension of the dataframe
dim(df)
dim(df_state)

# Check the first 6 rows
head(df) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
head(df_state) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)

# Examine the statistics data
summary(df) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
summary(df_state) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
```

#### Handle missing/duplicate values
#### In this part of data cleaning step, it was found out that there was missing data in some of the columns in "df" dataset while there was none in "df_state". The rows with missing data were data recorded for year 2020 and it was not being taken into consideration for predicting daily active cases because data in year 2020 was not of interest for this project.

```{r handle_missing, echo=TRUE, results='markup', result='asis'}
# Check for the columns with missing values
colSums(is.na(df)) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
colSums(is.na(df_state)) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)

# Show first few rows of the missing values
head(df[rowSums(is.na(df)) > 0, ]) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
head(df[rowSums(is.na(df_state)) > 0, ]) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)

# The missing rows for df can be ignored as there are 2020 data. 2021 data contains more columns.
# There is no missing rows for df_state.

# Check for duplicate values
df[duplicated(df)]
df[duplicated(df_state)]

# There are no duplicated rows
```

#### Preprocessing

```{r preprocessing, echo=TRUE, results='markup', result='asis'}
# Change date type from String to Date
df$date <- as.Date(df$date, format = "%Y-%m-%d")
df_state$date <- as.Date(df_state$date, format = "%Y-%m-%d")
```

#### Total Cases

```{r total_cases, echo=TRUE, results='markup', class.source = 'fold-hide'}
  df_total_cases <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    mutate(cases_total = cases_total / 1000) %>%
    arrange(state) %>%
    dplyr::rename(NAME_1 = state)

  malaysia_map <- data.table::copy(malaysia)
  malaysia_map@data <- join(malaysia_map@data, df_total_cases, by = "NAME_1")
  malaysia_df <- fortify(malaysia_map)
  malaysia_df <- join(malaysia_df, malaysia_map@data, by = "id")

  # https://garthtarr.github.io/meatR/ggplot_extensions.html
  # https://rstudio-pubs-static.s3.amazonaws.com/160207_ebe47475bb7744429b9bd4c908e2dc45.html
  ggplot() +
    geom_polygon(data = malaysia_df, aes(x = long, y = lat, group = group, fill = cases_total), color = "white", size = 0.25) +
    theme(aspect.ratio = 2 / 5) +
    scale_fill_distiller(name = "No. of Total Cases (in '000)", palette = "YlOrRd", direction = 1, breaks = pretty_breaks(n = 5)) +
    labs(title = "Total Cases Since Day 1") +
    theme_opts


  df_total_cases <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    arrange(desc(cases_total))
```

#### Infection Rate

```{r infection_rate, echo=TRUE, results='markup', class.source = 'fold-hide'}
  df_infection_rate <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    dplyr::rename(NAME_1 = state) %>%
    join(df_population, by = "NAME_1") %>%
    mutate(rate = cases_total / pop) %>%
    arrange(NAME_1)

  malaysia_map <- data.table::copy(malaysia)
  malaysia_map@data <- join(malaysia_map@data, df_infection_rate, by = "NAME_1")
  malaysia_df <- fortify(malaysia_map)
  malaysia_df <- join(malaysia_df, malaysia_map@data, by = "id")

  # https://garthtarr.github.io/meatR/ggplot_extensions.html
  # https://rstudio-pubs-static.s3.amazonaws.com/160207_ebe47475bb7744429b9bd4c908e2dc45.html
  ggplot() +
    geom_polygon(data = malaysia_df, aes(x = long, y = lat, group = group, fill = rate), color = "white", size = 0.25) +
    theme(aspect.ratio = 2 / 5) +
    scale_fill_distiller(name = "No. of Total Cases (%)", palette = "YlOrRd", direction = 1, breaks = pretty_breaks(n = 5), labels = percent) +
    labs(title = "Infection Rate based on Total Population") +
    theme_opts

  df_infection_rate <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    dplyr::rename(NAME_1 = state) %>%
    join(df_population, by = "NAME_1") %>%
    dplyr::rename(state = NAME_1) %>%    
    mutate(rate = cases_total / pop) %>%
    arrange(desc(rate)) %>%
    mutate(rate = paste0(round(cases_total / pop * 100, 2), "%"))
```

# ARIMA (Kamal)

```{r data_cleaning}
# Performing ARIMA on the number of COVID cases in Malaysia
# Aim to predict the next 60 days of new cases based on historical data
# A bit of cleaning
mycovidnewcases = df_country[,c(1:2)]
colnames(mycovidnewcases)
str(mycovidnewcases)
head(mycovidnewcases)

mycovidnewcases$date = as.Date(mycovidnewcases$date, format = "%d/%m/%Y")

covidplot = ggplot(mycovidnewcases, aes(date, cases_new)) +
  geom_line()
covidplot
```

### Plot ACF and PACF to understand the correlation in a time series data.
### Autocorrelation is the correlation between a time series and a delayed version of itself (lag).
### Autocorrelation Function (ACF) plots the correlation coefficient against the lag.
### The Partial Autocorrelation captures a 'direct' correlation between time series and a lagged version of itself

```{r check_seasonal_and_differencing}
# Perform ADF and KPSS test to check stationarity
# Null hypothesis is that the series is not stationary.

adf = adf.test(mycovidnewcases[,2])
adf
kpss = kpss.test(mycovidnewcases[,2])
kpss
```

### The ADF and KPSS test suggests that the data is non-stationary and differencing is required.

# Split data into train and test set. 

```{r split_train_test}
training = mycovidnewcases[1:500,]
test = mycovidnewcases[501:709,]
```

# Check how many differencing is needed

```{r check_differencing}

ndiffs(training[,2])  # Differencing of one is required but ARIMA model will do this for us as long as we input correct order (value of d)

```

# Use auto.arima to find out best model

```{r auto_arima}
summary(auto.arima(training[,2], trace = TRUE, ic = 'aicc', approximation = FALSE, stepwise = FALSE)) # Best model and order: ARIMA (3,1,2)
```

# Train the model with selected ARIMA model

```{r train_model}
trainingmodel = Arima(training[,2], order = c(3,1,2))
summary(trainingmodel)
coeftest(trainingmodel)
acf(trainingmodel$residuals)
```

# Make prediction using test set with the training model

```{r prediction}
testpred = forecast(test[,2], model = trainingmodel, h = 60, levels = c(95))
summary(testpred)
plot(testpred)
grid(nx = NULL, ny = NULL,
     lty = 2,
     col = 'gray',
     lwd = 2)
accuracy(testpred)
```

# With rolling average,

# Rolling average of 7

```{r rolling_7}
mycovidroll7 = mycovidnewcases %>%
  mutate(seven_avg = rollmean(mycovidnewcases[,2], 7, align = 'left', fill = 0)) %>%
  relocate(seven_avg)

head(mycovidroll7)

ggplot(mycovidroll7, aes(date, mycovidnewcases[,2])) + 
  geom_col(fill = 'pink') + 
  geom_line(aes(y = seven_avg), color = 'red', size = 0.75) +
  geom_line(aes(y = mycovidnewcases[,2]), color = 'blue', size = 1) + 
  labs(title = 'MY COVID data', y = 'covid cases')
```

# Rolling average of 21 

```{r rolling_21}
mycovidroll21 = mycovidnewcases %>%
  mutate(twoone_avg = rollmean(mycovidnewcases[,2], 21, align = 'left', fill = 0)) %>%
  relocate(twoone_avg)

ggplot(mycovidroll21, aes(date, mycovidnewcases[,2])) + 
  geom_col(fill = 'pink') + 
  geom_line(aes(y = mycovidroll7$seven_avg), color = 'red', size = 0.75) +
  geom_line(aes(y = mycovidnewcases[,2]), color = 'blue', size = 1) + 
  geom_line(aes(y = twoone_avg), color = 'green', size = 0.9) +
  labs(title = 'MY COVID data', y = 'covid cases')

tail(mycovidroll21, 30)
```

# ADF and KPSS test

```{r adfkpss}
adf21 = adf.test(mycovidroll21[,3])
adf21
kpss21 = kpss.test(mycovidroll21[,3])
kpss21

training21 = mycovidroll21[1:480,]
test21 = mycovidroll21[481:688,]
```

# Check differencing

```{r differencing}
ndiffs(training21[,3]) # one differencing
```

# Find best ARIMA model

```{r autoarima}
summary(auto.arima(training21[,3], trace = TRUE, ic = 'aicc', approximation = FALSE, stepwise = FALSE)) # Best model and order: ARIMA (2,1,2)
```

# Train model

```{r train}
trainingmodel21 = Arima(training21[,3], order = c(2,1,2))
summary(trainingmodel)
coeftest(trainingmodel)
acf(trainingmodel$residuals)
```

# Make prediction

```{r prediction_rolling21}
testpred21 = forecast(test21[,3], model = trainingmodel21, h = 30, levels = c(95))
summary(testpred21)
plot(testpred21)
grid(nx = NULL, ny = NULL,
     lty = 2,
     col = 'gray',
     lwd = 2)
accuracy(testpred21)
```

# Linear Regression

## Regression Preprocess

```{r regression_preprocess, echo=TRUE}
split_ratio <- 0.7
set.seed(168)
split_index <- createDataPartition(df_data$cases_new, p=split_ratio, list=FALSE)
data_train <- df_data[split_index,]
data_test <- df_data[-split_index,]
```

## Linear Regression Model Training (Gaussian Normal Distribution)

```{r linear_train, echo=TRUE}
linear_model <- lm(cases_new~cases_active,data=data_train)
summary(linear_model)
plot(linear_model)
```

```{r linear_prediction, echo=TRUE}
linear_prediction <- linear_model %>% predict(data_test)
linear_compare <- data.frame(actual=data_test$cases_new, predicted=linear_prediction)
head(linear_compare)
```

## Poisson Regression Model Training

```{r posson_train, echo=TRUE}
poisson_model <- glm(cases_new~cases_active, data=data_train, family=poisson(link="log"))
summary(poisson_model)

```

```{r poisson_prediction, echo=TRUE}
poisson_prediction <- poisson_model %>% predict(data_test)
poisson_compare <- data.frame(actual=data_test$cases_new, predicted=poisson_prediction)
head(poisson_compare)
```

## Performance Comparison

```{r linear_performance, echo=TRUE}
linear_performance <- data.frame(
  MODEL = "Gaussian Linear",
  R2 = R2(linear_prediction, data_test$cases_new),
  RMSE = RMSE(linear_prediction, data_test$cases_new),
  MAE = MAE(linear_prediction, data_test$cases_new)
)
linear_performance
```

```{r poisson_performance, echo=TRUE}
poisson_performance <- data.frame(
  MODEL = "Poisson GLM",
  R2 = R2(poisson_prediction, data_test$cases_new),
  RMSE = RMSE(poisson_prediction, data_test$cases_new),
  MAE = MAE(poisson_prediction, data_test$cases_new)
)
poisson_performance
```

## Performance Charts

```{r linear_performance_chart, echo=TRUE, fig.width=14, fig.height=8}
# Chart init
df_linear_predicted <- data.frame(date=data_test$date, cases_new=linear_prediction)
df_actual <- data_test
df_train <- data_train

lm_chart <- plot_ly()
# Predicted Data
lm_chart <- lm_chart %>% 
  add_trace(
    x = df_linear_predicted[["date"]], y = df_linear_predicted[["cases_new"]],
    name = "Predicted Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red', width = 3)
  )
# Test Data
lm_chart <- lm_chart %>% 
  add_trace(
    x = df_actual[["date"]], y = df_actual[["cases_new"]],
    name = "Actual Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'skyblue', width = 3)
  )

lm_chart <- lm_chart %>% 
  add_trace(
    x = df_train[["date"]], y = df_train[["cases_new"]], 
    name = "Train Data",
    type = "scatter",
    mode = "lines",
    line = list(color = 'green', width = 2)
  )

# Set figure title, x and y-axes titles
lm_chart <- lm_chart %>% layout(
  title = "Linear Regression of Daily New Cases",
  xaxis = list(title="Recorded Time"),
  yaxis = list(title="Daily Count of New Cases")
)%>%
  layout(plot_bgcolor='#e5ecf6',
          xaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff'),
          yaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff')
          )


lm_chart
```

```{r poisson_chart, echo=TRUE, fig.width=14, fig.height=8}
# Chart init
df_poisson_predicted <- data.frame(date=data_test$date, cases_new=poisson_prediction)

poisson_chart <- plot_ly()
# Predicted Data
poisson_chart <- poisson_chart %>% 
  add_trace(
    x = df_poisson_predicted[["date"]], y = df_poisson_predicted[["cases_new"]],
    name = "Predicted Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red', width = 3)
  )
# Test Data
poisson_chart <- poisson_chart %>% 
  add_trace(
    x = df_actual[["date"]], y = df_actual[["cases_new"]],
    name = "Actual Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'skyblue', width = 3)
  )

poisson_chart <- poisson_chart %>% 
  add_trace(
    x = df_train[["date"]], y = df_train[["cases_new"]], 
    name = "Train Data",
    type = "scatter",
    mode = "lines",
    line = list(color = 'green', width = 1)
  )

# Set figure title, x and y-axes titles
poisson_chart <- poisson_chart %>% layout(
  title = "Poisson Regression of Daily New Cases",
  xaxis = list(title="Recorded Time"),
  yaxis = list(title="Daily Count of New Cases")
)%>%
  layout(plot_bgcolor='#e5ecf6',
          xaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff'),
          yaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff')
          )


poisson_chart
```

# Game Time with ARIMA

## Predict future new cases Using Predicted future active cases from ARIMA Model

```{r arima_preprocess, echo=TRUE, fig.width=14, fig.height=8}
init_year <- format(as.Date(df_data[1,1], format="%Y-%m-%d"),"%Y")
init_day <- yday(as.Date(df_data[1,1], format="%Y-%m-%d"))
data_arima <- ts(df_data$cases_active, start=c(init_year,init_day), frequency=365)
head(data_arima)
```

## ARIMA Training

```{r arima_train, echo=TRUE, fig.width=14, fig.height=8}
arima_model <- auto.arima(df_data$cases_active, trace = TRUE, ic = 'aicc', approximation = FALSE, stepwise = FALSE)
arima_model
```

## ARIMA Predict

```{r arima_predict, echo=TRUE, fig.width=14, fig.height=8}
forecast_length <- 30
arima_predict <- forecast(arima_model, forecast_length)
head(arima_predict)
plot(arima_predict, main = "Predicted Active Cases", col.main = "black")
```

# Mixed Model Prediction with ARIMA

## Combined Prediction Start!

```{r combined_predict, echo=TRUE, fig.width=14, fig.height=8}
last_date <- as.Date(df_data[(nrow(df_data)):nrow(df_data),1], format="%Y-%m-%d")
last_date <- last_date + 1
df_arima <- data.frame(
  date=seq(last_date, by = "day", length.out = forecast_length),
  cases_active=arima_predict$mean
)
# Gaussian
combined_linear_prediction <- linear_model %>% predict(df_arima)
df_combined_linear_predicted <- data.frame(date=df_arima$date, cases_new=combined_linear_prediction)
# Poisson
combined_poisson_prediction <- poisson_model %>% predict(df_arima)
df_combined_poisson_predicted <- data.frame(date=df_arima$date, cases_new=combined_poisson_prediction)
```

## Smoothen data for nicer presentation

```{r smoothen_data, echo=TRUE, fig.width=14, fig.height=8}
df_data$month <- strftime(df_data$date, "%m")
df_data$year <- strftime(df_data$date, "%Y")

df_smooth <- df_data %>%                         
  group_by(date=lubridate::floor_date(df_data$date, "month")) %>% 
  dplyr::summarize(cases_new = mean(cases_new)) %>% 
  data.frame
```

## Showtime!

```{r combined_linear_results, echo=TRUE, fig.width=14, fig.height=8}
combined_linear_chart <- plot_ly()
# Predicted Data
combined_linear_chart <- combined_linear_chart %>% 
  add_trace(
    x = df_combined_linear_predicted[["date"]], y = df_combined_linear_predicted[["cases_new"]],
    name = "Future Predicted Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red', width = 3)
  )
# Test Data
combined_linear_chart <- combined_linear_chart %>% 
  add_trace(
    x = df_smooth[["date"]], y = df_smooth[["cases_new"]],
    name = "Actual Data (Rolled to Monthly)",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'skyblue', width = 3)
  )
# Set figure title, x and y-axes titles
combined_linear_chart <- combined_linear_chart %>% layout(
  title = "Prediction of Daily New Cases (Gaussian)",
  xaxis = list(title="Recorded Time"),
  yaxis = list(title="Daily Count of New Cases")
)%>%
  layout(plot_bgcolor='#e5ecf6',
          xaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff'),
          yaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff')
          )

combined_linear_chart
```

```{r combined_poisson_predict, echo=TRUE, fig.width=14, fig.height=8}
combined_poisson_chart <- plot_ly()
# Predicted Data
combined_poisson_chart <- combined_poisson_chart %>% 
  add_trace(
    x = df_combined_poisson_predicted[["date"]], y = df_combined_poisson_predicted[["cases_new"]],
    name = "Future Predicted Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red', width = 3)
  )
# Test Data
combined_poisson_chart <- combined_poisson_chart %>% 
  add_trace(
    x = df_smooth[["date"]], y = df_smooth[["cases_new"]],
    name = "Actual Data (Rolled to Monthly)",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'skyblue', width = 3)
  )
# Set figure title, x and y-axes titles
combined_poisson_chart <- combined_poisson_chart %>% layout(
  title = "Prediction of Daily New Cases (Poisson)",
  xaxis = list(title="Recorded Time"),
  yaxis = list(title="Daily Count of New Cases")
)%>%
  layout(plot_bgcolor='#e5ecf6',
          xaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff'),
          yaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff')
          )

combined_poisson_chart
```

It seems like the Poisson model is really bad just by the sight of looking at the graph. Therefore do not relies too much on statistical benchmark such as R2 as the source of truth. The easiest way to determine on hindsight is to visualize, use them! 

# Final Thoughts

### According to our models, COVID cases will continue to decline if large events such as the General Election, mass gatherings, and other unplanned occurrences do not occur.

### The following table is the comparison of performance for all our models:

```{r performance_charts, echo=TRUE, results='markup'}
arima_performance <- data.frame(
  MODEL = "ARIMA",
  R2 = "NaN",
  RMSE = accuracy(testpred)[, c("RMSE")],
  MAE =  accuracy(testpred)[, c("MAE")]
)
combined_performance <- rbind(linear_performance, poisson_performance, arima_performance)
kable(combined_performance)
```

### Note: Arima model’s R2 is not the same metric that can be used for comparison among the models.

### It appears that Gaussian Linear model is the best among the 3 models, we hope that our prediction model will help our government to raise awareness among the general public on the effectiveness of COVID-19 prevention measures implementation done.

###Stay safe!

# Thank you!




