---
title: "ARIMA"
author: "Chai Kau Yu, Davion"
date: "`r format(Sys.time(), '%d/%m/%y')`"
output:
    prettydoc::html_pretty:
    theme: HPSTR
    highlight: github
    math: katex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

# Performing ARIMA on the number of COVID cases in Malaysia
# Aim to predict the next 60 days of new cases based on historical data

# import libraries

```{r Requirements, echo=TRUE, results='hide', message=FALSE}
if (!require('readxl')) install.packages('readxl'); library('readxl')
if (!require('dplyr')) install.packages('dplyr'); library('dplyr')
if (!require('ggplot2')) install.packages('ggplot2'); library('ggplot2')
if (!require('lubridate')) install.packages('lubridate'); library('lubridate')
if (!require('forecast')) install.packages('forecast'); library('forecast')
if (!require('fpp')) install.packages('fpp'); library('fpp')
if (!require('tseries')) install.packages('tseries'); library('tseries')
```

# Import dataset

```{r data_ingestion, echo=TRUE}
mycovid <- read.csv("./cases_malaysia.csv")

head(mycovid)
colnames(mycovid)
```
# A bit of cleaning

```{r data_cleaning, echo=TRUE}
mycovidnewcases <- mycovid[,c(1:2)]
colnames(mycovidnewcases)
str(mycovidnewcases)

mycovidnewcases$date <- as.Date(mycovidnewcases$date, format = "%Y-%m-%d")
mycovidnewcases
```

# Plot graph to see trends

```{r data_plot, echo=TRUE}
covidplot <- ggplot(mycovidnewcases, aes(date, cases_new)) + geom_line()
covidplot
```

# Plot ACF and PACF to understand the correlation in a time series data.
# Autocorrelation is the correlation between a time series and a delayed version of itself (lag).
# Autocorrelation Function (ACF) plots the correlation coefficient against the lag.
# The Partial Autocorrelation captures a 'direct' correlation between time series and a lagged version of itself
```{r ts_plot, echo=TRUE}
tsdisplay(mycovidnewcases)
# seasonplot(mycovidnewcases) # Data is not seasonal
```

```{r ts_test, echo=TRUE}
# Perform ADF and KPSS test to check stationarity
# Null hypothesis is that the series is not stationary.

adf = adf.test(mycovidnewcases[,2])
adf
# kpss = kpss.test(tsdata2)
kpss = kpss.test(mycovidnewcases[,2])
kpss
```

# the ADF and KPSS test suggests that the data is non-stationary and differencing is required.
# Split data into train and test set. 

```{r ts_split, echo=TRUE}
training = mycovidnewcases[1:600,]
test = mycovidnewcases[601:709,]
```

# Check how many differencing is needed

```{r ts_diff, echo=TRUE}
ndiffs(training[,2])  # Differencing of two is required but ARIMA model will do this for us as long as we input correct order (value of d)

# Use auto.arima to find out best model

summary(auto.arima(training[,2], trace = TRUE, ic = 'aicc', approximation = FALSE, stepwise = FALSE)) # Best model and order: ARIMA (4,2,1)

# Train the model with selected ARIMA model

trainingmodel = Arima(training[,2], order = c(4,2,1))
summary(trainingmodel)
coeftest(trainingmodel)
acf(trainingmodel$residuals)
```

# Make prediction using test set with the training model

```{r ts_predict, echo=TRUE}
testpred = forecast(test[,2], model = trainingmodel, h = 60, levels = c(95))
summary(testpred)
plot(testpred)
grid(nx = NULL, ny = NULL,
     lty = 2,
     col = 'gray',
     lwd = 2)
accuracy(testpred)
```

# END NORMAL



# With rolling average,

```{r Requirements_rolling, echo=TRUE, results='hide', message=FALSE}
if (!require('zoo')) install.packages('zoo'); library('zoo')
```

# Rolling average of 7

```{r roll_plot, echo=TRUE}
mycovidroll7 = mycovidnewcases %>%
  mutate(seven_avg = rollmean(mycovidnewcases[,2], 7, align = 'left', fill = 0)) %>%
  relocate(seven_avg)

head(mycovidroll7)

ggplot(mycovidroll7, aes(date, mycovidnewcases[,2])) + 
  geom_col(fill = 'pink') + 
  geom_line(aes(y = seven_avg), color = 'red', size = 0.75) +
  geom_line(aes(y = mycovidnewcases[,2]), color = 'blue', size = 1) + 
  labs(title = 'MY COVID data', y = 'covid cases')
```

# Rolling average of 21 

```{r roll_plot_2, echo=TRUE}
mycovidroll21 = mycovidnewcases %>%
  mutate(twoone_avg = rollmean(mycovidnewcases[,2], 21, align = 'left', fill = 0)) %>%
  relocate(twoone_avg)

ggplot(mycovidroll21, aes(date, mycovidnewcases[,2])) + 
  geom_col(fill = 'pink') + 
  geom_line(aes(y = mycovidroll7$seven_avg), color = 'red', size = 0.75) +
  geom_line(aes(y = mycovidnewcases[,2]), color = 'blue', size = 1) + 
  geom_line(aes(y = twoone_avg), color = 'green', size = 0.9) +
  labs(title = 'MY COVID data', y = 'covid cases')

tail(mycovidroll21, 30)

adf21 = adf.test(mycovidroll21[,3])
adf21
kpss21 = kpss.test(mycovidroll21[,3])
kpss21

training21 = mycovidroll21[1:550,]
test21 = mycovidroll21[551:688,]

ndiffs(training21[,3]) # two differencing

summary(auto.arima(training21[,3], trace = TRUE, ic = 'aicc', approximation = FALSE, stepwise = FALSE)) # Best model and order: ARIMA (3,2,2)

trainingmodel21 = Arima(training21[,3], order = c(3,2,2))
summary(trainingmodel)
coeftest(trainingmodel)
acf(trainingmodel$residuals)

testpred21 = forecast(test21[,3], model = trainingmodel21, h = 30, levels = c(95))
summary(testpred21)
plot(testpred21)
grid(nx = NULL, ny = NULL,
     lty = 2,
     col = 'gray',
     lwd = 2)
accuracy(testpred21)
```

# END


