---
title: "Linear Regression plot + result table + elevator pitch"
author: |
  | Chai Kau Yu, Davion (S2019226)
  | William Heng Chun Meng (S2005592)
  | Lim Mei Cee (17162537)
  | Kamal Suria Asri Raja (S2110703)
  | Hong Zi Shen (S2114600)
date: "`r format(Sys.time(), '%d/%m/%y')`"
output:
    prettydoc::html_pretty:
    theme: HPSTR
    highlight: github
    math: katex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

### R packages to be used.

```{r Requirements, echo=TRUE, results='hide', message=FALSE}
if (!require('dplyr')) install.packages('dplyr'); library('dplyr')
if (!require('tidyr')) install.packages('tidyr'); library('tidyr')
if (!require('lubridate')) install.packages('lubridate'); library('lubridate')
if (!require('tidyquant')) install.packages('tidyquant'); library('tidyquant')
if (!require('plotly')) install.packages('plotly'); library('plotly')
# Training
if (!require('caret')) install.packages('caret'); library('caret')
# Time Series (ARIMA)
if (!require('forecast')) install.packages('forecast'); library('forecast')
# Moving Average
if (!require('zoo')) install.packages('zoo'); library('zoo')
```

# Data Import

```{r data_ingestion, echo=TRUE, results='markup'}
df_country <- read.csv("./cases_malaysia.csv", header=TRUE)
# Convert date column & sort
df_country$date <- as.Date(df_country$date, format="%Y-%m-%d")
df_country <- df_country[order(df_country$date),]
# Filter data
df_data <- df_country[,c("date", "cases_new", "cases_active")]
```

# Linear train

```{r lm_train, echo=TRUE}
split_ratio <- 0.7
set.seed(168)
split_index <- createDataPartition(df_data$cases_new, p=split_ratio, list=FALSE)
data_train <- df_data[split_index,]
data_test <- df_data[-split_index,]

linear_model <- lm(cases_new~cases_active,data=data_train)
summary(linear_model)
plot(linear_model)
```

```{r linear_prediction, echo=TRUE}
linear_prediction <- linear_model %>% predict(data_test)
linear_compare <- data.frame(actual=data_test$cases_new, predicted=linear_prediction)
head(linear_compare)
```

```{r linear_performance, echo=TRUE}
linear_performance <- data.frame(
  MODEL = "Gaussian Linear",
  R2 = R2(linear_prediction, data_test$cases_new),
  RMSE = RMSE(linear_prediction, data_test$cases_new),
  MAE = MAE(linear_prediction, data_test$cases_new)
)
linear_performance
```


```{r linear_performance_chart, echo=TRUE, fig.width=14, fig.height=8}
# Chart init
df_predicted <- data.frame(date=data_test$date, cases_new=linear_prediction)
df_actual <- data_test
df_train <- data_train

lm_chart <- plot_ly()
# Predicted Data
lm_chart <- lm_chart %>% 
  add_trace(
    x = df_predicted[["date"]], y = df_predicted[["cases_new"]],
    name = "Predicted Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red', width = 3)
  )
# Test Data
lm_chart <- lm_chart %>% 
  add_trace(
    x = df_actual[["date"]], y = df_actual[["cases_new"]],
    name = "Actual Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'skyblue', width = 3)
  )

lm_chart <- lm_chart %>% 
  add_trace(
    x = df_train[["date"]], y = df_train[["cases_new"]], 
    name = "Train Data",
    type = "scatter",
    mode = "lines",
    line = list(color = 'green', width = 2)
  )

# Set figure title, x and y-axes titles
lm_chart <- lm_chart %>% layout(
  title = "Linear Regression of Daily New Cases",
  xaxis = list(title="Recorded Time"),
  yaxis = list(title="Daily Count of New Cases")
)%>%
  layout(plot_bgcolor='#e5ecf6',
          xaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff'),
          yaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff')
          )


lm_chart
```

# Predict future new cases Using Predicted future active cases from ARIMA Model

```{r arima_preprocess, echo=TRUE, fig.width=14, fig.height=8}
init_year <- format(as.Date(df_data[1,1], format="%Y-%m-%d"),"%Y")
init_day <- yday(as.Date(df_data[1,1], format="%Y-%m-%d"))
data_arima <- ts(df_data$cases_active, start=c(init_year,init_day), frequency=365)
head(data_arima)
```

# ARIMA Training

```{r arima_train, echo=TRUE, fig.width=14, fig.height=8}
arima_model <- auto.arima(df_data$cases_active, trace = TRUE, ic = 'aicc', approximation = FALSE, stepwise = FALSE)
arima_model
```

```{r arima_predict, echo=TRUE, fig.width=14, fig.height=8}
forecast_length <- 30
arima_predict <- forecast(arima_model, forecast_length)
head(arima_predict)
plot(arima_predict, main = "Predicted Active Cases", col.main = "black")
```

```{r combined_predict, echo=TRUE, fig.width=14, fig.height=8}
last_date <- as.Date(df_data[(nrow(df_data)):nrow(df_data),1], format="%Y-%m-%d")
last_date <- last_date + 1
df_arima <- data.frame(
  date=seq(last_date, by = "day", length.out = forecast_length),
  cases_active=arima_predict$mean
)

combined_prediction <- linear_model %>% predict(df_arima)
df_combined_predicted <- data.frame(date=df_arima$date, cases_new=combined_prediction)
```

```{r smoothen_data, echo=TRUE, fig.width=14, fig.height=8}
df_data$month <- strftime(df_data$date, "%m")
df_data$year <- strftime(df_data$date, "%Y")

df_smooth <- df_data %>%                         
  group_by(date=lubridate::floor_date(df_data$date, "month")) %>% 
  dplyr::summarize(cases_new = mean(cases_new)) %>% 
  data.frame
```

```{r combined_results, echo=TRUE, fig.width=14, fig.height=8}
combined_chart <- plot_ly()
# Predicted Data
combined_chart <- combined_chart %>% 
  add_trace(
    x = df_combined_predicted[["date"]], y = df_combined_predicted[["cases_new"]],
    name = "Future Predicted Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red', width = 3)
  )
# Test Data
combined_chart <- combined_chart %>% 
  add_trace(
    x = df_smooth[["date"]], y = df_smooth[["cases_new"]],
    name = "Actual Data (Rolled to Monthly)",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'skyblue', width = 3)
  )
# Set figure title, x and y-axes titles
combined_chart <- combined_chart %>% layout(
  title = "Prediction of Daily New Cases (Gaussian)",
  xaxis = list(title="Recorded Time"),
  yaxis = list(title="Daily Count of New Cases")
)%>%
  layout(plot_bgcolor='#e5ecf6',
          xaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff'),
          yaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff')
          )

combined_chart
```

# Fiddling with Poisson

```{r posson_train, echo=TRUE, fig.width=14, fig.height=8}
poisson_model <- glm(cases_new~cases_active, data=data_train, family=poisson(link="log"))
summary(poisson_model)
# plot(gamma_model)

poisson_prediction <- poisson_model %>% predict(data_test)
poisson_compare <- data.frame(actual=data_test$cases_new, predicted=poisson_prediction)
head(poisson_compare)

poisson_performance <- data.frame(
  MODEL = "Poisson GLM",
  R2 = R2(poisson_prediction, data_test$cases_new),
  RMSE = RMSE(poisson_prediction, data_test$cases_new),
  MAE = MAE(poisson_prediction, data_test$cases_new)
)
poisson_performance
```

```{r poisson_chart, echo=TRUE, fig.width=14, fig.height=8}
# Chart init
df_predicted <- data.frame(date=data_test$date, cases_new=poisson_prediction)

poisson_chart <- plot_ly()
# Predicted Data
poisson_chart <- poisson_chart %>% 
  add_trace(
    x = df_predicted[["date"]], y = df_predicted[["cases_new"]],
    name = "Predicted Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red', width = 3)
  )
# Test Data
poisson_chart <- poisson_chart %>% 
  add_trace(
    x = df_actual[["date"]], y = df_actual[["cases_new"]],
    name = "Actual Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'skyblue', width = 3)
  )

poisson_chart <- poisson_chart %>% 
  add_trace(
    x = df_train[["date"]], y = df_train[["cases_new"]], 
    name = "Train Data",
    type = "scatter",
    mode = "lines",
    line = list(color = 'green', width = 1)
  )

# Set figure title, x and y-axes titles
poisson_chart <- poisson_chart %>% layout(
  title = "Poisson Regression of Daily New Cases",
  xaxis = list(title="Recorded Time"),
  yaxis = list(title="Daily Count of New Cases")
)%>%
  layout(plot_bgcolor='#e5ecf6',
          xaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff'),
          yaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff')
          )


poisson_chart
```
### It seems like the Poisson model is really bad just by the sight of looking at the graph. Therefore do not relies too much on statistical benchmark such as R2 as the source of truth. The easiest way to determine on hindsight is to visualize, use them! 

# Poisson Prediction

```{r combined_predict_poisson, echo=TRUE, fig.width=14, fig.height=8}
combined_prediction <- poisson_model %>% predict(df_arima)
df_combined_predicted <- data.frame(date=df_arima$date, cases_new=combined_prediction)

combined_chart <- plot_ly()
# Predicted Data
combined_chart <- combined_chart %>% 
  add_trace(
    x = df_combined_predicted[["date"]], y = df_combined_predicted[["cases_new"]],
    name = "Future Predicted Data",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red', width = 3)
  )
# Test Data
combined_chart <- combined_chart %>% 
  add_trace(
    x = df_smooth[["date"]], y = df_smooth[["cases_new"]],
    name = "Actual Data (Rolled to Monthly)",
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'skyblue', width = 3)
  )
# Set figure title, x and y-axes titles
combined_chart <- combined_chart %>% layout(
  title = "Prediction of Daily New Cases (Poisson)",
  xaxis = list(title="Recorded Time"),
  yaxis = list(title="Daily Count of New Cases")
)%>%
  layout(plot_bgcolor='#e5ecf6',
          xaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff'),
          yaxis = list(
            zerolinecolor = '#ffff',
            zerolinewidth = 2,
            gridcolor = 'ffff')
          )

combined_chart
```


```{r compare_performance, echo=TRUE, fig.width=14, fig.height=8}
poisson_performance
linear_performance
combined_performance <- rbind(linear_performance, poisson_performance)
combined_performance 
```

### End of document





