---
title: "A Deep Analysis of Malaysian Covid-19 Cases in 2021"
author: |
  | Chai Kau Yu, Davion (S2019226)
  | William Heng Chun Meng (S2005592)
  | Lim Mei Cee (17162537)
  | Kamal Suria Asri Raja (S2110703)
  | Hong Zi Shen (S2114600)
date: "`r format(Sys.time(), '%d/%m/%y')`"
output:
  prettydoc::html_pretty:
    theme: HPSTR
    highlight: github
    math: katex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, results="hide")
```
TODO: Refine title

## Initial Questions
TODO: Must have at least two questions. It is best to have different types of problems, ie one regression, and one classification

1. 
2.

## Objective
TODO: Analysis: Identify the questions, what is the objective/goal of processing this dataset? What answers are you interested to find through this dataset.<br>
TODO: Determine the details about the dataset (eg. title, year, the purpose of dataset, dimension content, structure, summary) by exploring the raw data.<br>
TODO: Short introduction with objective of the project.<br>

## Data Cleaning and Preprocessing
TODO: Which section of the data do you need to tidy?<br>
TODO: Prepare data for analysis by correcting the variables and contents of the data.<br>
TODO: Putting it all together as a new cleaned/processed dataset: For this task, you are also encouraged to explore any cleaning packages in R other than those learned in the course (diplyr, tidyr, lubridate, etc).<br>

* Step 1 : Import libraries
* Step 2 : Import dataset
* Step 3 : Handle missing/duplicate
* Step 4 : Preprocessing

#### Import libraries

```{r import_libraries, message=FALSE, warning=FALSE}
# if (!require('dplyr'))
#  install.packages('dplyr', repos='https://cran.asia/');
if (!require('kableExtra'))
  install.packages('kableExtra', repos='https://cran.asia/');
# if (!require('lubridate'))
#   install.packages('lubridate', repos='https://cran.asia/');
if (!require('plotly'))
  install.packages('plotly', repos='https://cran.asia/');
if (!require('plyr'))
  install.packages('plyr', repos='https://cran.asia/');
if (!require('raster'))
  install.packages('raster', repos='https://cran.asia/');
if (!require('scales'))
  install.packages('scales', repos='https://cran.asia/');
# if (!require('tidyquant'))
#   install.packages('tidyquant', repos='https://cran.asia/');
# if (!require('tidyr'))
#   install.packages('tidyr', repos='https://cran.asia/');


# library(dplyr)
library(kableExtra)
# library(lubridate)
library(plotly)
library(plyr)
library(raster)
library(scales)
# library(tidyquant)
# library('tidyr')
```

#### Import dataset

```{r import_dataset, echo=TRUE, results='markup', result='asis'}
# covid_malaysia_endpoint <- 'https://raw.githubusercontent.com/MoH-Malaysia/covid19-public/main/epidemic/cases_malasia.csv'
# covid_state_endpoint <- 'https://raw.githubusercontent.com/MoH-Malaysia/covid19-public/main/epidemic/cases_state.csv'
covid_malaysia_endpoint <- 'cases_malaysia.csv'
covid_state_endpoint <- 'cases_state.csv'

df <- read.csv(covid_malaysia_endpoint, header=TRUE)
df_state <- read.csv(covid_state_endpoint, header=TRUE)

# Check the structure of the dataframe
str(df)
str(df_state)

# Check the dimension of the dataframe
dim(df)
dim(df_state)

# Check the first 6 rows
head(df) %>% kable('html') %>% kable_styling(font_size = 12)
head(df_state) %>% kable('html') %>% kable_styling(font_size = 12)

# Examine the statistics data
summary(df) %>% kable('html') %>% kable_styling(font_size = 12)
summary(df_state) %>% kable('html') %>% kable_styling(font_size = 12)
```

#### Handle missing/duplicate values

```{r handle_missing, echo=TRUE, results='markup', result='asis'}
# Check for the columns with missing values
colSums(is.na(df)) %>% kable('html') %>% kable_styling(font_size = 12)
colSums(is.na(df_state)) %>% kable('html') %>% kable_styling(font_size = 12)

# Show first few rows of the missing values
head(df[rowSums(is.na(df)) > 0,]) %>% kable('html') %>% kable_styling(font_size = 12)
head(df[rowSums(is.na(df_state)) > 0,]) %>% kable('html') %>% kable_styling(font_size = 12)

# The missing rows for df can be ignored as there are 2020 data. 2021 data contains more columns.
# There is no missing rows for df_state.

# Check for duplicate values
df[duplicated(df)]
df[duplicated(df_state)]

# There are no duplicated rows
```

#### Preprocessing

```{r preprocessing, echo=TRUE, results='markup', result='asis'}
df$date <- as.Date(df$date, format='%Y-%m-%d')
df_state$date <- as.Date(df_state$date, format='%Y-%m-%d')
```

## Exploratory Data Analysis
TODO: Results may include visualization, prediction, evaluation of models and discussion of output

#### A brief Look on the graph 

```{r time_series, echo=TRUE, results='markup'}
fig <- plot_ly(df, type = 'scatter', mode = 'lines')%>%
  add_trace(x = ~date, y = ~cases_new, name = 'Daily New Cvoid Cases')%>%
  layout(showlegend = F)
options(warn = -1)

fig <- fig %>%
  layout(
         xaxis = list(zerolinecolor = '#ffff',
                      zerolinewidth = 2,
                      gridcolor = 'ffff'),
         yaxis = list(zerolinecolor = '#ffff',
                      zerolinewidth = 2,
                      gridcolor = 'ffff'),
         plot_bgcolor='#e5ecf6', width = 1200)


fig
```

#### Density Map

```{r denity_map, echo=TRUE, results='markup'}

df_state <- df_state %>%
  mutate(date = as.Date(df_state$date, format = "%Y-%m-%d")) %>%
  filter(date == as.Date('2021-09-01')) %>%
  mutate(state = replace(state, state == "W.P. Kuala Lumpur", "Kuala Lumpur")) %>%
  mutate(state = replace(state, state == "W.P. Labuan", "Labuan")) %>%
  mutate(state = replace(state, state == "W.P. Putrajaya", "Putrajaya")) %>%
  arrange(state) %>%
  dplyr::rename(NAME_1 = state)
  
malaysia <- getData("GADM", country = "MYS", level = 1)
malaysia@data$id <- rownames(malaysia@data)
malaysia@data <- join(malaysia@data, df_state, by = "NAME_1")
malaysia_df <- fortify(malaysia)
malaysia_df <- join(malaysia_df, malaysia@data, by = "id")

theme_opts <- list(theme(
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  plot.background = element_blank(),
  axis.line = element_blank(),
  axis.text.x = element_blank(),
  axis.text.y = element_blank(),
  axis.ticks = element_blank(),
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  plot.title = element_blank()
))

# https://garthtarr.github.io/meatR/ggplot_extensions.html
# https://rstudio-pubs-static.s3.amazonaws.com/160207_ebe47475bb7744429b9bd4c908e2dc45.html
ggplot() +
  geom_polygon(data = malaysia_df, aes(x = long, y = lat, group = group, fill = cases_new), color = "white", size = 0.25) +
  theme(aspect.ratio = 2/5) +
  scale_fill_distiller(name = "No. of New Cases", palette = "YlOrRd", direction=1, breaks = pretty_breaks(n = 5)) +
  labs(title = paste('Number of New Cases in Each State on', '2021-09-01'))
```

## Machine Learning
TODO: Results may include visualization, prediction, evaluation of models and discussion of output

## Conclusion
TODO: Conclusion

## Presentation and Submission
TODO Report: Submission will be an R markdown published at Rpubs, and the link is to be submitted in spectrum. The R markdown may include the following:

*	Short introduction with objective of the project.
*	Explanation of all the processes involved in the project
*	Results may include visualization, prediction, evaluation of models and discussion of output
*	Conclusion

TODO: Only one member per group will submit the report.<br>
TODO: Each group is required to prepare a 10 minute presentation with powerpoint.<br>
TODO: Both group members must present their parts.

## End of Report