---
title: "A Deep Analysis of Malaysian Covid-19 Cases in 2021"
author: |
  | Chai Kau Yu, Davion (S2019226)
  | William Heng Chun Meng (S2005592)
  | Lim Mei Cee (17162537)
  | Kamal Suria Asri Raja (S2110703)
  | Hong Zi Shen (S2114600)
date: "`r format(Sys.time(), '%d/%m/%y')`"
runtime: shiny
output:
  html_document:
    theme: 
      bootswatch: "spacelab"
    code_folding: show
# output: html_document
#   prettydoc::html_pretty:
#     theme: lumen
#     highlight: github
#     math: katex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, results = "hide")
```

```{r, echo = FALSE}
bslib::bs_themer()
thematic::thematic_shiny(font = "auto")
```

TODO: Refine title

## Initial Questions
TODO: Must have at least two questions. It is best to have different types of problems, ie one regression, and one classification

1. 
2.

## Objective
TODO: Analysis: Identify the questions, what is the objective/goal of processing this dataset? What answers are you interested to find through this dataset.<br>
TODO: Determine the details about the dataset (eg. title, year, the purpose of dataset, dimension content, structure, summary) by exploring the raw data.<br>
TODO: Short introduction with objective of the project.<br>

## Data Cleaning and Preprocessing
TODO: Which section of the data do you need to tidy?<br>
TODO: Prepare data for analysis by correcting the variables and contents of the data.<br>
TODO: Putting it all together as a new cleaned/processed dataset: For this task, you are also encouraged to explore any cleaning packages in R other than those learned in the course (diplyr, tidyr, lubridate, etc).<br>

#### Import libraries

```{r import_libraries, message=FALSE, warning=FALSE}
if (!require("dplyr")) {
  install.packages("dplyr", repos = "https://cran.asia/")
}
if (!require("kableExtra")) {
  install.packages("kableExtra", repos = "https://cran.asia/")
}
# if (!require("lubridate"))
#   install.packages("lubridate", repos="https://cran.asia/");
if (!require("plotly")) {
  install.packages("plotly", repos = "https://cran.asia/")
}
if (!require("plyr")) {
  install.packages("plyr", repos = "https://cran.asia/")
}
if (!require("raster")) {
  install.packages("raster", repos = "https://cran.asia/")
}
if (!require("scales")) {
  install.packages("scales", repos = "https://cran.asia/")
}
if (!require("shiny")) {
  install.packages("shiny", repos = "https://cran.asia/")
}
if (!require("thematic")) {
  install.packages("thematic", repos = "https://cran.asia/")
}
# if (!require("tidyquant"))
#   install.packages("tidyquant", repos="https://cran.asia/");
# if (!require("tidyr"))
#   install.packages("tidyr", repos="https://cran.asia/");

library(dplyr)
library(kableExtra)
# library(lubridate)
library(plotly)
library(plyr)
library(raster)
library(scales)
library(shiny)
# library(tidyquant)
# library(tidyr)
```

#### Data Ingestion

```{r data_ingestion, echo=TRUE, results='markup', result='asis'}
# covid_malaysia_endpoint <- "https://raw.githubusercontent.com/MoH-Malaysia/covid19-public/main/epidemic/cases_malasia.csv"
# covid_state_endpoint <- "https://raw.githubusercontent.com/MoH-Malaysia/covid19-public/main/epidemic/cases_state.csv"
covid_malaysia_endpoint <- "cases_malaysia.csv"
covid_state_endpoint <- "cases_state.csv"

df <- read.csv(covid_malaysia_endpoint, header = TRUE)
df_state <- read.csv(covid_state_endpoint, header = TRUE)
```

#### Data Initialization

```{r data_initialization, echo=TRUE, results='markup', result='asis'}
df_population <- data.frame(
  c("Selangor", "Sabah", "Johor", "Sarawak", "Perak", "Kedah", "Kelantan", "Pulau Pinang", "W.P. Kuala Lumpur", "Pahang", "Terengganu", "Negeri Sembilan", "Melaka", "Perlis", "W.P. Putrajaya", "W.P. Labuan"),
  c(6555400, 3833000, 3794000, 2822200, 2508900, 2194100, 1928800, 1774400, 1746600, 1684600, 1275100, 1129100, 937500, 255400, 116100, 100100)
)
colnames(df_population) <- c("NAME_1", "pop")

theme_opts <- list(theme(
  panel.grid.minor = element_blank(),
  panel.grid.major = element_blank(),
  panel.background = element_blank(),
  plot.background = element_blank(),
  axis.line = element_blank(),
  axis.text.x = element_blank(),
  axis.text.y = element_blank(),
  axis.ticks = element_blank(),
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  plot.title = element_blank()
))

malaysia <- getData("GADM", country = "MYS", level = 1)
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Trengganu", "Terengganu"))
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Kuala Lumpur", "W.P. Kuala Lumpur"))
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Labuan", "W.P. Labuan"))
malaysia@data <- mutate(malaysia@data, NAME_1 = replace(NAME_1, NAME_1 == "Putrajaya", "W.P. Putrajaya"))
malaysia@data$id <- rownames(malaysia@data)
```

#### Data Inspection

```{r data_inspection, echo=TRUE, results='markup', result='asis'}
# Check the structure of the dataframe
str(df)
str(df_state)

# Check the dimension of the dataframe
dim(df)
dim(df_state)

# Check the first 6 rows
head(df) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
head(df_state) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)

# Examine the statistics data
summary(df) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
summary(df_state) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
```

#### Handle missing/duplicate values

```{r handle_missing, echo=TRUE, results='markup', result='asis'}
# Check for the columns with missing values
colSums(is.na(df)) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
colSums(is.na(df_state)) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)

# Show first few rows of the missing values
head(df[rowSums(is.na(df)) > 0, ]) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)
head(df[rowSums(is.na(df_state)) > 0, ]) %>%
  kable("html") %>%
  scroll_box(width = "100%") %>%
  kable_styling(font_size = 12)

# The missing rows for df can be ignored as there are 2020 data. 2021 data contains more columns.
# There is no missing rows for df_state.

# Check for duplicate values
df[duplicated(df)]
df[duplicated(df_state)]

# There are no duplicated rows
```

#### Preprocessing

```{r preprocessing, echo=TRUE, results='markup', result='asis'}
# Change date type from String to Date
df$date <- as.Date(df$date, format = "%Y-%m-%d")
df_state$date <- as.Date(df_state$date, format = "%Y-%m-%d")
```

## Exploratory Data Analysis
TODO: Results may include visualization, prediction, evaluation of models and discussion of output

#### A brief Look on the graph 

```{r time_series, echo=TRUE, results='markup'}
fig <- plot_ly(df, type = "scatter", mode = "lines") %>%
  add_trace(x = ~date, y = ~cases_new, name = "Daily New Cvoid Cases") %>%
  layout(showlegend = F)
options(warn = -1)

fig <- fig %>%
  layout(
    xaxis = list(
      zerolinecolor = "#ffff",
      zerolinewidth = 2,
      gridcolor = "ffff"
    ),
    yaxis = list(
      zerolinecolor = "#ffff",
      zerolinewidth = 2,
      gridcolor = "ffff"
    ),
    plot_bgcolor = "#e5ecf6", width = 1200
  )


fig
```

#### Total Cases

```{r total_cases, echo=TRUE, results='markup', class.source = 'fold-hide'}
renderPlot({
  df_total_cases <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    mutate(cases_total = cases_total / 1000) %>%
    arrange(state) %>%
    dplyr::rename(NAME_1 = state)

  malaysia_map <- data.table::copy(malaysia)
  malaysia_map@data <- join(malaysia_map@data, df_total_cases, by = "NAME_1")
  malaysia_df <- fortify(malaysia_map)
  malaysia_df <- join(malaysia_df, malaysia_map@data, by = "id")

  # https://garthtarr.github.io/meatR/ggplot_extensions.html
  # https://rstudio-pubs-static.s3.amazonaws.com/160207_ebe47475bb7744429b9bd4c908e2dc45.html
  ggplot() +
    geom_polygon(data = malaysia_df, aes(x = long, y = lat, group = group, fill = cases_total), color = "white", size = 0.25) +
    theme(aspect.ratio = 2 / 5) +
    scale_fill_distiller(name = "No. of Total Cases (in '000)", palette = "YlOrRd", direction = 1, breaks = pretty_breaks(n = 5)) +
    labs(title = "Total Cases Since Day 1") +
    theme_opts
})

renderTable({
  df_total_cases <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    arrange(desc(cases_total))
  return(df_total_cases)
})
```

#### Infection Rate

```{r infection_rate, echo=TRUE, results='markup', class.source = 'fold-hide'}
renderPlot({
  df_infection_rate <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    dplyr::rename(NAME_1 = state) %>%
    join(df_population, by = "NAME_1") %>%
    mutate(rate = cases_total / pop) %>%
    arrange(NAME_1)

  malaysia_map <- data.table::copy(malaysia)
  malaysia_map@data <- join(malaysia_map@data, df_infection_rate, by = "NAME_1")
  malaysia_df <- fortify(malaysia_map)
  malaysia_df <- join(malaysia_df, malaysia_map@data, by = "id")

  # https://garthtarr.github.io/meatR/ggplot_extensions.html
  # https://rstudio-pubs-static.s3.amazonaws.com/160207_ebe47475bb7744429b9bd4c908e2dc45.html
  ggplot() +
    geom_polygon(data = malaysia_df, aes(x = long, y = lat, group = group, fill = rate), color = "white", size = 0.25) +
    theme(aspect.ratio = 2 / 5) +
    scale_fill_distiller(name = "No. of Total Cases (%)", palette = "YlOrRd", direction = 1, breaks = pretty_breaks(n = 5), labels = percent) +
    labs(title = "Infection Rate based on Total Population") +
    theme_opts
})

renderTable({
  df_infection_rate <- df_state %>%
    group_by(state) %>%
    summarise_at(vars(cases_new), list(cases_total = sum)) %>%
    dplyr::rename(NAME_1 = state) %>%
    join(df_population, by = "NAME_1") %>%
    dplyr::rename(state = NAME_1) %>%    
    mutate(rate = cases_total / pop) %>%
    arrange(desc(rate)) %>%
    mutate(rate = paste0(round(cases_total / pop * 100, 2), "%"))
  return(df_infection_rate)
})
```

#### Daily Active Cases (Interactive)

```{r daily_active_cases, echo=TRUE, results='markup', class.source = 'fold-hide'}
dateInput("date", "Date", value = "2021-09-01")
data <- eventReactive(input$date, {
  df_daily_cases <- df_state %>%
    mutate(date = as.Date(df_state$date, format = "%Y-%m-%d")) %>%
    filter(date == as.Date(input$date)) %>%
    arrange(state) %>%
    dplyr::rename(NAME_1 = state)

  malaysia_map <- data.table::copy(malaysia)
  malaysia@data <- join(malaysia@data, df_daily_cases, by = "NAME_1")
  malaysia_df <- fortify(malaysia)
  malaysia_df <- join(malaysia_df, malaysia@data, by = "id")

  return(list('map' = malaysia_df, 'table' = df_daily_cases))
})

renderPlot({
  # https://garthtarr.github.io/meatR/ggplot_extensions.html
  # https://rstudio-pubs-static.s3.amazonaws.com/160207_ebe47475bb7744429b9bd4c908e2dc45.html
  ggplot() +
    geom_polygon(data = data()$map, aes(x = long, y = lat, group = group, fill = cases_new), color = "white", size = 0.25) +
    theme(aspect.ratio = 2 / 5) +
    scale_fill_distiller(name = "No. of New Cases", palette = "YlOrRd", direction = 1, breaks = pretty_breaks(n = 5)) +
    labs(title = paste("Number of New Cases in Each State on", input$date))
})

renderTable({
  df_daily_cases <- data()$table %>% dplyr::rename(state = NAME_1) %>% arrange(desc(cases_new))
  df_daily_cases[, c("state", "cases_new")]
})
```

## Machine Learning
TODO: Results may include visualization, prediction, evaluation of models and discussion of output

## Conclusion
TODO: Conclusion

## Presentation and Submission
TODO Report: Submission will be an R markdown published at Rpubs, and the link is to be submitted in spectrum. The R markdown may include the following:

*	Short introduction with objective of the project.
*	Explanation of all the processes involved in the project
*	Results may include visualization, prediction, evaluation of models and discussion of output
*	Conclusion

TODO: Only one member per group will submit the report.<br>
TODO: Each group is required to prepare a 10 minute presentation with powerpoint.<br>
TODO: Both group members must present their parts.

## End of Report
