---
title: "A Deep Analysis of Malaysian Covid-19 Cases in 2021"
author: |
  | Chai Kau Yu, Davion (S2019226)
  | William Heng Chun Meng (S2005592)
  | Lim Mei Cee (17162537)
  | Kamal Suria Asri Raja (S2110703)
  | Hong Zi Shen (S2114600)
date: "`r format(Sys.time(), '%d/%m/%y')`"
output:
  prettydoc::html_pretty:
    theme: HPSTR
    highlight: github
    math: katex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, results="hide")
```
TODO: Refine title

## Initial Questions
TODO: Must have at least two questions. It is best to have different types of problems, ie one regression, and one classification

1. 
2.

## Objective
TODO: Analysis: Identify the questions, what is the objective/goal of processing this dataset? What answers are you interested to find through this dataset.<br>
TODO: Determine the details about the dataset (eg. title, year, the purpose of dataset, dimension content, structure, summary) by exploring the raw data.<br>
TODO: Short introduction with objective of the project.<br>

## Data Cleaning and Preprocessing
TODO: Which section of the data do you need to tidy?<br>
TODO: Prepare data for analysis by correcting the variables and contents of the data.<br>
TODO: Putting it all together as a new cleaned/processed dataset: For this task, you are also encouraged to explore any cleaning packages in R other than those learned in the course (diplyr, tidyr, lubridate, etc).<br>

```{r requirements_check, message=FALSE, warning=FALSE}
# # if (!require('dplyr')) install.packages('dplyr'); library('dplyr')
# # if (!require('tidyr')) install.packages('tidyr'); library('tidyr')
if (!require('lubridate'))
  install.packages('lubridate');
if (!require('tidyquant'))
  install.packages('tidyquant', repos='https://cran.asia/');
if (!require('plotly'))
  install.packages('plotly', repos='https://cran.asia/');

library('lubridate')
library('plotly')
library('tidyquant')
```

#### Data Ingestion

```{r data_ingestion, echo=TRUE, results='markup'}
# covid_malaysia_endpoint <- "https://raw.githubusercontent.com/MoH-Malaysia/covid19-public/main/epidemic/cases_malaysia.csv"
covid_malaysia_endpoint <- 'cases_malaysia.csv'
covid_malaysia_df <- read.csv(covid_malaysia_endpoint, header=TRUE)
covid_malaysia_df$date <- as.Date(covid_malaysia_df$date, format="%Y-%m-%d")
str(covid_malaysia_df)
dim(covid_malaysia_df)
```

## Exploratory Data Analysis
TODO: Results may include visualization, prediction, evaluation of models and discussion of output

#### A brief Look on the graph 

```{r time_series, echo=TRUE, results='markup'}
fig <- plot_ly(covid_malaysia_df, type = 'scatter', mode = 'lines')%>%
  add_trace(x = ~date, y = ~cases_new, name = 'Daily New Cvoid Cases')%>%
  layout(showlegend = F)
options(warn = -1)

fig <- fig %>%
  layout(
         xaxis = list(zerolinecolor = '#ffff',
                      zerolinewidth = 2,
                      gridcolor = 'ffff'),
         yaxis = list(zerolinecolor = '#ffff',
                      zerolinewidth = 2,
                      gridcolor = 'ffff'),
         plot_bgcolor='#e5ecf6', width = 1200)


fig
```

## Machine Learning
TODO: Results may include visualization, prediction, evaluation of models and discussion of output

## Conclusion
TODO: Conclusion

## Presentation and Submission
TODO Report: Submission will be an R markdown published at Rpubs, and the link is to be submitted in spectrum. The R markdown may include the following:

*	Short introduction with objective of the project.
*	Explanation of all the processes involved in the project
*	Results may include visualization, prediction, evaluation of models and discussion of output
*	Conclusion

TODO: Only one member per group will submit the report.<br>
TODO: Each group is required to prepare a 10 minute presentation with powerpoint.<br>
TODO: Both group members must present their parts.

## End of Report